Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-17 manuscript/climate_sensitivity_draft.Rmd
small updates

*To characterize how environmental conditions vary with height, data were obtained from the NEON tower located <1km from the study area via the neonUtilities package [@R-neonUtilities]. We used wind speed, relative humidity, and air temperature data, all measured over a vertical profile spanning heights from 7.2 m to above the top of the tree canopy (31.0 or 51.8m, depending on censor), for the years 2016-2018 [@neon_national_2018]. After filtering for missing and outlier values, we determined the daily minima and maxima, which we then aggregated at the monthly scale.* **(work on organization of this.)**

@@

@@

Analyses focused on testing the predictions presented in Table 1, with $Rt$ (or $Rt_{ARIMA}$) as the response variable. 
Models were run for all drought years combined and for each drought year individually. 
The general statistical model for hypothesis testing was a mixed effects model, implemented  in the lme4 package in R [**REF**], with $Rt$ (or $Rt_{ARIMA}$) as the response variable, tree nested within species as a random effect, and independent variables as specified below. 
In the multi-year model only, we also included a fixed effect of drought year. (**IAN, CONFIRM THIS**))
We used AICc to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. 
AICc refers to a corrected version of AICc, and is best suited for small data sizes [see @brewer_relative_2016].

@@

Crown position varied as expected with height (dominant > co-dominant > intermediate > suppressed), but with substantial variation (Fig. **2d**). 
Correlation between height and canopy position was 0.73.

@@

Responses varied across species and by drought (Fig. **3**). 
Averaged across all droughts, $Rt$ was lowest in *Liriodendron tulipifera* (mean $Rt$ = **0.66**) and highest in *Fagus grandifolia* (mean $Rt$ = **0.99**).

@@

Species traits... (Table 2, Fig. **S4**)

>>>>

@@

To characterize how environmental conditions vary with height, data were obtained from the NEON tower located <1km from the study area via the neonUtilities package [@R-neonUtilities]. We used wind speed, relative humidity, and air temperature data, all measured over a vertical profile spanning heights from 7.2 m to above the top of the tree canopy (31.0 or 51.8m, depending on censor), for the years 2016-2018 [@neon_national_2018]. After filtering for missing and outlier values, we determined the daily minima and maxima, which we then aggregated at the monthly scale.*

@@

Analyses focused on testing the predictions presented in Table 1, with $Rt$ (or $Rt_{ARIMA}$) as the response variable. 
Models were run for all drought years combined and for each drought year individually. 
The general statistical model for hypothesis testing was a mixed effects model, implemented  in the lme4 package in R [**REF**], with $Rt$ (or $Rt_{ARIMA}$) as the response variable, tree nested within species as a random effect, and independent variables as specified below. 
In the multi-year model, we also included a fixed effect of drought year. (**IAN, CONFIRM THIS**))
We used AICc to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. 
AICc refers to a corrected version of AICc, and is best suited for small data sizes [see @brewer_relative_2016].

@@

Crown position varied as expected with height (dominant > co-dominant > intermediate > suppressed), but with substantial variation (Fig. **2d**). 
*Correlation between height and canopy position was 0.73.*

@@

@@

Species traits... (Table 2, Fig. **S4**)
Responses varied across species and by drought (Fig. **3**). 
Averaged across all droughts, $Rt$ was lowest in *Liriodendron tulipifera* (mean $Rt$ = **0.66**) and highest in *Fagus grandifolia* (mean $Rt$ = **0.99**).
